On the Functionality of the Multilayer Perceptron

### 2020-11-25 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Added New TDE features, updated Figures

\paragraph*{}In general, for an $N \times M$ input, with kernel size $m \times n$, with stride size $1 \times 1$, and $K$ feature maps.
\begin{equation}
f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(N \times M)} \rightarrow
x^{(l)} \in \mathbb{R}^{([N-n+1] \times [M-m+1] \times K)}
\end{equation}
As an example, consider a single filter map over input $x \in \mathbb{R}^{(4 \times 3)}$ and filter map $W \in \mathbb{R}^{(2 \times 2)}$ as shown in Fig. (\ref{fig-2DConvExample}):
\begin{figure}[H]
\begin{center}
	\begin{subfigure}{0.45\textwidth}
	\includegraphics[scale=0.6]{../figures/2DConvExample(a)}
	\caption{Input Activations}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
	\includegraphics[scale=0.6]{../figures/2DConvExample(b)}
	\caption{Convolution Filter}
	\end{subfigure}
	\begin{subfigure}{0.9\textwidth}
	\centering
	\includegraphics[scale=0.6]{../figures/2DConvExample(c)}
	\caption{Convolution Result}
	\end{subfigure}
\end{center}
\caption{The result of convolving an input (a) with an filter map (b) is a new set of activations (c). This Image was adapted from Goodfellow, pg. 325 \cite{Goodfellow}}
\label{fig-2DConvExample}
\end{figure}
Note that formal implementations include a bias vector and an activation function.

@@

\paragraph*{}Classification tasks require a set of inputs that are used to make the decision as to which class the sample belongs to. These inputs are called \textit{predictors} or \textit{features} \cite{James,Loy,Serizel}. Features are quantitative, low-dimensional representations of each sample that convey key characteristics of the sample. 
Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib discusses the vitality of feature selection \cite{Khan}:
\begin{quote}
The data reduction stage which is also called feature extraction, consists of discovering a few important facts about each class. The choice of features is critical as it greatly affects the accuracy of audio classification. 
\end{quote}
In the biological process of categorizing sound sources, the time-domain waveform is usually enough to match the sound to a source \cite{Olson}. However, a computer representation of a waveform is an array-like structure of values sampled discretely in time and volume \cite{Virtanen,Liu}. Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks \cite{Serizel}. We must develop a set of features or predictors that can describe important properties of the waveform in an efficient manner \cite{Goodfellow,James}.

@@

\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector. We have developed a set of predictors that describe each sample in a compact manner, with reasonable separation boundaries between samples from different classes.
These features are derived are principles of music, digital signal processing, previous work, and underlying physics that governs the behavior of instruments. In the following sections, we outline the set of $21$ features used in the classification process. For each feature, we visualize the distribution in across each class in the form as box-plots. Each feature has been normalize to have a zero mean, and unit-variance across all classes.

\textcolor{red}{Describe nature of features w/ separation boundaries}

@@

\paragraph*{}The application of neural networks to image-processing and recognition has been well studied and developed in the last few decades \cite{Geron,Goodfellow,Loy,Mierswa}. As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior. Following this success, it make senses to provide an image-like representation of a sound wave as a feature. We do this in the form of a \textit{spectrogram} matrix. A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time. In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis. Thus each point in the 2-Dimensional space is an energy at a given time and frequency. Examples spectrograms from the wave form data set are shown in Fig. (\ref{fig-spectrograms}).
\begin{figure}[H]
\begin{center}
\textcolor{red}{Insert spectrograms here}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=0.45\textwidth , height=0.2\textheight]{../Figures/AnalysisFrame}
	\caption{A section of a violin bowing an $A4$ note, $1024$ samples long}
	\end{subfigure}
\caption{Spectrogram representations of various waveforms}
\label{fig-spectrograms}
\end{center}
\end{figure}

@@

@@

\paragraph*{}Window functions are use to account for discontinuities that may arise in the waveform at the edges of each analysis frame. The Fourier Transform assumes that an integer number of signal periods fit within each analysis frame, however this is rarely the case. A transform of this kind of signal can lead to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins \textcolor{red}{Citation needed}. This result is a frequency domain that is not an accurate representation of the equivalent time domain. The Hanning window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.

@@

@@

\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Each feature is one element in the feature vector for the particular sample. For consistency between samples, each waveform is padded or truncated to contain the same number of samples $M$. Time space is indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$

@@

\paragraph*{}The time domain envelope (TDE) is a rough measurement of the energy contained in the time domain. If we divide the signal into analysis frames, as in Fig. (\ref{fig-AnalysisFrames}), then the TDE approximates the energy in that frame. A frame with a high TDE indicates a generally large amplitude, and a frame with a low TDE indicates a generally small amplitude. (i.e. the signal has not started or is decaying)

\paragraph*{}We adapt this TDE to \textbf{compute the time domain envelope of the full waveform}. Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE represents a consistent measurement of energy in the full time-domain signal \cite{Liu}. The TDE is computed as the RMS-Energy of the waveform, $s$ and is given by \cite{Olson,Serizel}:
\begin{equation}
\label{eqn-RMS}
\text{RMS}\big[ s \big] = \sqrt{\frac{1}{M} \sum_{i=0}^{M-1} s[i]^2}
\end{equation}
For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large TDE value. For instruments with short sustain times, such as plucked stings or dampened percussion we expect a comparably small TDE value \cite{Olson,White}. The difference allows for considerable separation between many percussion and woodwind classes.

\begin{figure}[H]
\begin{center}
%textcolor{red}{Plot of TDE Feature Here}
\includegraphics[scale=0.3]{../FiguresFeatures/Time_Domain_Env}
\end{center}
\caption{A comparison of the Time Domain Envelope across each class using a box-and-whisker plot}
\label{fig-FeatureTDE}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
%\textcolor{red}{PLOT OF ZXR FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/Zero_X-Rate}
\end{center}
\caption{A comparison of the Zero-Crossing Rate for each class using a box-and-whisker plot}
\label{fig-FeatureZXR}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
%\textcolor{red}{PLOT OF TCM FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/Time_Center_of_Mass}
\end{center}
\caption{A comparison of the temporal center mass for each class using a box-and-whisker plot}
\label{fig-FeatureTCM}
\end{figure}

@@

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/Auto_Correlation_1}
	\caption{ACC $k=1$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/Auto_Correlation_2}
	\caption{ACC $k=2$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/Auto_Correlation_3}
	\caption{ACC $k=3$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/Auto_Correlation_4}
	\caption{ACC $k=4$}
	\end{subfigure}

@@

\paragraph*{}Physically, MFCC's are a transform of a transform. This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes in the signal\cite{Virtanen}. Ceptrum coefficients are commonly used to speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.

@@

\begin{figure}[H]
\label{fig-FeatureFCM}
\begin{center}
%\textcolor{red}{PLOT OF FCM FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/Frequency_Center_of_Mass}
\end{center}
\caption{A comparison of the frequency center-of-mass for each class using box-and-whisker plots}
\end{figure}

@@

\FOR {$k = 0,1,2,3,...,K-2,K-1$}
	\item Reset all parameters in $F^*$ to a random "untrained" state
	\item Set aside testing data subset
	\item $X_{test} \leftarrow X^{(k)}$
	\item $Y_{test} \leftarrow Y^{(k)}$
	\item Concatenate the remaining subsets into training data set
	\item $X_{train} \leftarrow X^{(i \neq j)}$
	\item $Y_{train} \leftarrow Y^{(i \neq j)}$
	\item Train the model, $F^*$ with the $X_{train}$ and $Y_{train}$ subset.
	\item Evaluate the trained model with the $X_{test}$ and $Y_{test}$ data set, and compute value of metric function(s) $P$
	\item Store Performance $P$ in Performance History array
\ENDFOR \\
Compare performance results, and adjust model or parameters as needed, and repeat if desired. \\
Run additional analysis on performance metrics.
\end{algorithmic}
\end{algorithm}

@@

\end{quote}
Thus, indexes where $i = j$ represents a correct prediction, and $i \neq k$ indicates an incorrect prediction. A confusion matrix with relatively large values in main diagonal indicates a model that consistently predicts correct labels \cite{Geron}.  Below we present some "dummy" confusion matrices as numerical arrays, and a corresponding heat-map equivalent.

@@

	\begin{subfigure}[h]{\textwidth , 0.8\textheight}
	\begin{center}
	\textcolor{red}{Images of Confusion Matrices Go Here!} 
	\end{center}
	\end{subfigure}
	\begin{subfigure}[h]{\textwidth , 0.8\textheight}
	\begin{center}
	\textcolor{red}{Images of Confusion Matrices Go Here!} 
	\end{center}
	\end{subfigure}

\caption{Example Confusion Matrices for $k$-classes tasks}
\label{fig-DummyConfMat}
\end{figure}

@@

\paragraph*{}The confusion matrix can be a cumbersome, so often it is useful to express the performance in terms of more concise quantities. For this we use \textit{accuracy score}, \textit{precision score}, and \textit{recall score}.

@@

\paragraph*{}Precision score (also called \textit{specificity} or \textit{positive predictive value}) is the ratio of chosen elements to all relevant elements. This bounds precision to the range $(0,1)$, with a higher value more desirable. For a classifier with $k = 2$ unique classes, we define the precision score of a model as:
\begin{equation}
\label{eqn-BinaryPrecision}
\text{Prec} = \frac{TP}{TP + FP}
\end{equation}
Where $TP$ is the number of \textit{true-positive}, and $FP$ is the number of false-positive predictions. For a $k$-classes confusion matrix, $C$, the precision score of a class $j$, is given by the entry $C_{j,j}$ divided by the sum of row $j$:
\begin{equation}
\label{eqn-KPrecision}
\text{Prec}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{j,i}}
\end{equation}
For multi-class problems, we report the precision score as averaged over all $k$ classes.

\paragraph*{}The quantity $TP + FP$ is a measurement of the total number chosen items in that class. Thus, the quantity precision gives the ratio of correct selections to all selections that were made. More intuitively, we can describe precision as the fraction of selected items that are relevant to the problem at hand \cite{Geron}.

@@

\paragraph*{}Recall score (also called \textit{sensitivity} or \textit{true positive rate}) also offers a more concise performance metric than a confusion metric. For a classifier with $k = 2$ unique classes, we define the recall score of a model as:
\begin{equation}
\label{eqn-BinaryRecall}
\text{Recall} = \frac{TP}{TP + FN}
\end{equation}
Where $TP$ is the number of \textit{true-positive}, and $FN$ is the number of \textit{false-negative} predictions. For a $k$-classes confusion matrix, $C$, the precision score of a class $j$ is given by the entry $C_{j,j}$ divided by the sum of column $j$:
\begin{equation}
\label{eqn-KRecall}
\text{Recall}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{i,j}}
\end{equation}
For multi-class problems, we report the precision score as averaged over all $k$ classes.

\paragraph*{}The quantity $TP + FN$ is a measurement of the total number items in that class, independent of selection. Thus, the quantity recall gives the ratio of correct selections to all selections that were made. More intuitively, we can describe recall as the fraction of relevant items that were selected \cite{Geron}.

@@

\subsubsection{Accuracy Score}

\paragraph*{}Accuracy score, while not commonly used is the most intuitive of all of the performance metrics. It is the ratio of correct predictions of he total number of predictions. While immediately useful for equally sampled binary classification problems, it looses meaning as the number of classes increases, and epecially if the number of samples per class is not consistent \cite{Geron,James}.

@@

\paragraph*{}Despite this we can still sue accuracy score to provide a rough approximation for how the model is performing. \textcolor{red}{finish this!}

@@

>>>>

\paragraph*{}In general, for an $N \times M$ input, with kernel size $m \times n$, with stride size $1 \times 1$, and $K$ feature maps.
\begin{equation}
f^{(l)} : x^{(l-1)} \in \mathbb{R}^{(N \times M)} \rightarrow
x^{(l)} \in \mathbb{R}^{([N-n+1] \times [M-m+1] \times K)}
\end{equation}
As an example, consider a single filter map over input $x \in \mathbb{R}^{(4 \times 3)}$ and filter map $W \in \mathbb{R}^{(2 \times 2)}$ as shown in Fig. (\ref{fig-2DConvExample}):
\begin{figure}[H]
\begin{center}

	\begin{subfigure}{0.45\textwidth}
	\includegraphics[scale=0.6]{../figures/2DConvExample(a)}
	\caption{Input Activations}
	\end{subfigure}

	\begin{subfigure}{0.45\textwidth}
	\includegraphics[scale=0.6]{../figures/2DConvExample(b)}
	\caption{Convolution Filter}
	\end{subfigure}

	\begin{subfigure}{0.9\textwidth}
	\centering
	\includegraphics[scale=0.6]{../figures/2DConvExample(c)}
	\caption{Convolution Result}
	\end{subfigure}

\end{center}
\caption{The result of convolving an input (a) with an filter map (b) is a new set of activations (c). This Image was adapted from Goodfellow, pg. 325 \cite{Goodfellow}}
\label{fig-2DConvExample}
\end{figure}
Note that formal implementations include a bias vector and an activation function.

@@

\paragraph*{}Classification tasks require a set of inputs  . These inputs are called \textit{predictors} or \textit{features} \cite{James,Loy,Serizel}. Features are quantitative, low-dimensional representations of each sample that convey key characteristics of the sample. 
Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib discusses the vitality of feature selection \cite{Khan}:
\begin{quote}
The data reduction stage which is also called feature extraction, consists of discovering a few important facts about each class. The choice of features is critical as it greatly affects the accuracy of audio classification. 
\end{quote}
In the biological process of categorizing sound sources, the time-domain waveform is usually enough to match the sound to a source \cite{Olson}. However, a computer representation of a waveform is an array-like structure of values sampled discretely in time and volume \cite{Virtanen,Liu}. Presenting the raw time-series waveform to a model directly has experimentally shown to be unstable in for classification tasks so we must develop a set of features or predictors that can describe important properties of the waveform in an efficient manner \cite{Goodfellow,James,Serizel}.

@@

\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector. We have developed a set of predictors that describe each sample in a compact manner, with reasonable separation boundaries between samples from different classes.
These features are derived are principles of music, digital signal processing, previous work, and underlying physics that governs the behavior of instruments. In the following sections, we outline the set of $21$ features used in the classification process. For each feature, we visualize the distribution in across each class in the form as box-plots. Each feature has been normalized to have a zero mean, and unit-variance across all classes.

\subsubsection{Decision Boundaries}

\paragraph*{}A trained classifier makes a prediction in the form of a statistical likelihood of a sample belonging to a particular class \cite{Goodfellow,James}. A $k$- categories classifier contains $k$ output neurons, each one representing a class. When a set of features is presented to the classifier, the value contained within each neuron is the "confidence" on the interval $[0,1]$ that a sample belongs to that class. For example, if neuron $q$ has an activation value of $0.25$, we say that there is a $25\%$ chance that the sample belongs to class $q$. Most commonly, we take the neuron with the highest activation value to be the chosen class, even if the next highest activation is a close second \cite{Loy}.

\paragraph*{}This concept stems from the idea that a trained neural network classifier is basing its predictions by generating \textit{decision boundaries} in feature space \cite{Loy,James,Serizel}.

@@

\paragraph*{}The application of neural networks to image-processing and recognition has been well studied and developed in the last few decades \cite{Geron,Goodfellow,Loy,Mierswa}. As a result, model architectures for image processing related tasks are well-explored and have shown experimentally successful behavior. Following this success, it make senses to provide an image-like representation of a sound wave as a feature. We do this in the form of a \textit{spectrogram} matrix. A spectrogram is a representation of the energy distribution of a sound wave as a function of both frequency and time. In a conventional spectrogram, the passing of time is shown along the $x$-axis, and the frequency spectrum is shown on the $y$-axis. Thus each point in the 2-Dimensional space is an energy at a given time and frequency. Examples spectrograms from the wave form data set are shown in Fig. (\ref{fig-spectrograms}).
\begin{figure}[H]
\begin{center}
\textcolor{red}{Insert spectrograms here}
\caption{Spectrogram representations of various waveforms}
\label{fig-spectrograms}
\end{center}
\end{figure}

\subsubsection{Frame Blocking}
\label{subsubsec-FrameBlocking}

@@

\subsubsection{Windowing}
\label{subsubsec-Windowing}

@@

\paragraph*{}Window functions are use to account for discontinuities that may arise in the waveform at the edges of each analysis frame. The Fourier Transform assumes that an integer number of signal periods fit within each analysis frame, however this is rarely the case. Transforming a signal with to \textit{spectral leakage} where energy appears to "leak" into adjacent frequency bins \textcolor{red}{Citation needed}. This result is a frequency domain that is not an accurate representation of the equivalent time domain. The Hanning window uses the raised cosine function to taper the signal off to zero at the end-points, thus eliminate discontinuities at the edges while weighting the samples at the center much more heavily.

@@

\subsubsection{Discrete Fourier Transform}
\label{subsubsec-DFT}

@@

\paragraph*{}The features described in this section are derived from time-domain representations of each audio sample. Each feature is one element in the feature vector for the particular sample. For consistency between samples, each waveform is padded or truncated to contain the same number of samples $M$. The number of samples $M$ is chosen to correspond the number of sample needed to make the $N \times k$ spectrogram matrix. This way,t he spectrogram and time-series features are representative of the same time interval in the file sample. Time space is indexed by $s[i]$ with $i \in [0,1,2,3,...,M-2,M-1]$

@@

\paragraph*{}The time domain envelope (TDE) is a rough measurement of the energy contained in the time domain. If we divide the signal into analysis frames, as in Fig. (\ref{fig-AnalysisFrames}), then the TDE approximates the energy in that frame. A frame with a high TDE indicates a generally large amplitude, and a frame with a low TDE indicates a generally small amplitude, i.e. the signal has not started or is decaying. The small size of each analysis frame makes computing a TDE for each impractical, and create a very high-dimensional feature vector. This would also cause problems as some waveforms may have an initial attack that differs in time by a few analysis frames. Computing TDE for each frame would therefore introduce temporal bias, as the same waveform delayed by a few milliseconds would generate a wildly different set of predictor values \cite{Serizel}.

\paragraph*{}One way to mitigate this is to group analysis frames together and compute the TDE of a collection of frames. This way, small most waveforms will produce an identical set of features to a time-delayed version of itself. By choosing a sufficiently large number of TDE values, we can also generate n approximation of than amplitude envelope of the time-series waveform. This comes at a higher computational cost, and a previously mentioned higher dimensional feature vector

\paragraph*{}We adapt this TDE to \textbf{compute the time domain envelope over $5$ non-overlapping analysis frames}. Since the maximum amplitude of each waveform array has been normalized to $\pm 1$, the TDE represents a consistent measurement of energy in each waveform subset. \cite{Liu}. The TDE is computed as the RMS-Energy of the waveform, $s$ and the $j$-th TDE value is given by \cite{Olson,Serizel}:
\begin{equation}
\label{eqn-RMS}
\text{TDE}_j\big[ s \big] = \sqrt{\frac{1}{Q} \sum_{i=n}^{n+Q} s[i]^2}
\end{equation}
For instruments with long sustain or release times, such as strings or undampened mallet percussion, we expect a comparably large TDE value. For instruments with short sustain times, such as plucked stings or dampened percussion we expect a comparably small TDE value \cite{Olson,White}. The difference allows for considerable separation between many percussion and woodwind classes.

\begin{figure}[H]
\begin{center}
%textcolor{red}{Plot of TDE Feature Here}
\includegraphics[scale=0.3]{../FiguresFeatures/TDE}
\end{center}
\caption{A comparison of the Time Domain Envelope across each class using a box-and-whisker plot}
\label{fig-FeatureTDE}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
%\textcolor{red}{PLOT OF ZXR FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/ZXR}
\end{center}
\caption{A comparison of the Zero-Crossing Rate for each class using a box-and-whisker plot}
\label{fig-FeatureZXR}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
%\textcolor{red}{PLOT OF TCM FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/TCM}
\end{center}
\caption{A comparison of the temporal center mass for each class using a box-and-whisker plot}
\label{fig-FeatureTCM}
\end{figure}

@@

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/ACC_1}
	\caption{ACC $k=1$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/ACC_2}
	\caption{ACC $k=2$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/ACC_3}
	\caption{ACC $k=3$}
	\end{subfigure}

	\begin{subfigure}{1.0\textwidth}
	\centering
	\includegraphics[width=\textwidth , height=0.2\textheight]
		{../FiguresFeatures/ACC_4}
	\caption{ACC $k=4$}
	\end{subfigure}

@@

\paragraph*{}Physically, MFCC's are a transform of a transform. This allows us to investigate the periodicity of the frequency spectrum, which highlights phenomena such as overtones or echoes in the signal\cite{Virtanen}. Cepstrum coefficients are commonly used to speech identification and are very prolific in sound recognition tasks \cite{Serizel,Sahidullah,Liu}.

@@

\begin{figure}[H]
\label{fig-FeatureFCM}
\begin{center}
%\textcolor{red}{PLOT OF FCM FEATURES HERE}
\includegraphics[scale=0.3]{../FiguresFeatures/FCM}
\end{center}
\caption{A comparison of the frequency center-of-mass for each class using box-and-whisker plots}
\end{figure}

@@

\FOR {$k = 0,1,2,3,...,K-2,K-1$}
	\item Reset all parameters in $F^*$ to a random "untrained" state
	\item Set aside testing data subset
	\item $X_{test} \leftarrow X^{(k)}$
	\item $Y_{test} \leftarrow Y^{(k)}$
	\item Concatenate the remaining subsets into training data set
	\item $X_{train} \leftarrow X^{(i \neq k)}$
	\item $Y_{train} \leftarrow Y^{(i \neq k)}$
	\item Train the model, $F^*$ with the $X_{train}$ and $Y_{train}$ subset.
	\item Evaluate the trained model with the $X_{test}$ and $Y_{test}$ data set, and compute value of metric function(s) $P$
	\item Store Performance $P$ in Performance History array
\ENDFOR \\
Compare performance results, and adjust model or parameters as needed, and repeat if desired. \\
Run additional analysis on performance metrics.
\end{algorithmic}
\end{algorithm}

@@

\end{quote}
Thus, indexes where $i = j$ represents a correct prediction, and $i \neq k$ indicates an incorrect prediction. A confusion matrix with relatively large values in main diagonal indicates a model that predicts correct labels \cite{Geron}.  Below we present some synthetic confusion matrices, which combine the counts in each index and a corresponding color map.

@@

	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{../FiguresMetrics/StdConfA}
	\caption{Diagonal dominance indicates a stronger classifier}
	\end{subfigure}
	\hfill	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{../FiguresMetrics/StdConfB}
	\caption{No diagonal dominance indicates a weaker classifier}
	\end{subfigure}

\caption{Example Confusion Matrices for $4$-categories classifier}
\label{fig-DummyConfMat}
\end{figure}

@@

\paragraph*{}However, it is more useful to weight the confusion matrix according to class occurrence. For example, if we had a $2 \times 2$ matrix with entries $100$ and $20$ in the main diagonal, it seems that class $A$ has a much higher prediction success than class $B$. However, if there are $200$ elements in class $A$, and only $21$ in class $B$, then we see that class $A$ has a $50\%$ classification rate, while class $B$ has a $95\%$ classification rate, To Combat this, we typically normalize each confusion matrix by the number of samples in each "actual" class. Put simply, we all elements in a given row by the sum of that row.

\paragraph*{}The confusion matrix can be a cumbersome, so often it is useful to express the performance in terms of more concise quantities. For this we use \textit{accuracy score}, \textit{precision score}, \textit{F1-score}, and \textit{recall score}. These metrics are standard in the field of machine-learning classification and are often useful for identifying different strengths and weaknesses in each model \cite{Geron,James}.

@@

\paragraph*{}Precision score (also called \textit{specificity} or \textit{positive predictive value}) is the ratio of chosen elements to all relevant elements. This bounds precision to the range $(0,1)$, with a higher value more desirable. For a classifier with $k = 2$ unique classes, we define the precision score of a model as:
\begin{equation}
\label{eqn-BinaryPrecision}
\text{Prec} = \frac{TP}{TP + FP}
\end{equation}
Where $TP$ is the number of \textit{true-positive}, and $FP$ is the number of false-positive predictions. For a $k$-classes confusion matrix, $C$, the precision score of a class $j$, is given by the entry $C_{j,j}$ divided by the sum of row $j$:
\begin{equation}
\label{eqn-KPrecision}
\text{Prec}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{j,i}}
\end{equation}
In the case of a multi-class classifier, the precision score represents an\textit{one-vs-all} measurement. This means that for any class $j$, the sample belongs to class $j$ or it does not. All other classes, $i \neq j$ are temporarily considered to be a single aggregated class. The quantity $TP + FP$, or the sum over the confusion matrix row is a measurement of the total number of items that are predicted to be in the given class. Therefore the precision metric answers the question: \textit{"How many selected items are relevant to the problem?"} \cite{Geron,James}.

@@

\paragraph*{}Recall score (also called \textit{sensitivity} or \textit{true positive rate}) also offers a more concise performance metric than a confusion metric. For a classifier with $k = 2$ unique classes, we define the recall score of a model as:
\begin{equation}
\label{eqn-BinaryRecall}
\text{Recall} = \frac{TP}{TP + FN}
\end{equation}
Where $TP$ is the number of \textit{true-positive}, and $FN$ is the number of \textit{false-negative} predictions. For a $k$-classes confusion matrix, $C$, the precision score of a class $j$ is given by the entry $C_{j,j}$ divided by the sum of column $j$:
\begin{equation}
\label{eqn-KRecall}
\text{Recall}_j = \frac{C_{j,j}}{\sum_{i=0}^{k-1}C_{i,j}}
\end{equation}
In the case of a multi-class classifier, the recall score also represents an\textit{one-vs-all} measurement. This means that for any class $j$, the sample belongs to class $j$ or it does not. All other classes, $i \neq j$ are again temporarily considered to be a single aggregated class. The quantity $TP + FN$, or the sum over the confusion matrix coumn is a measurement of the total number of items that are actually in the given class. Therefore the recall metric answers the question: \textit{"How many relevant items to the problem are selected?"} \cite{Geron,James}.

\subsection{Micro F1-Score}

@@

\subsubsection{Accuracy Score \&}

\paragraph*{}Accuracy score, while not commonly used is the most intuitive of all of the performance metrics. It is the ratio of correct predictions of he total number of predictions. While immediately useful for equally sampled binary classification problems, it looses meaning as the number of classes increases, and epecially if the number of samples per class is not consistent \cite{Geron}.

@@

\paragraph*{}Accuracy score of model is defined:
\begin{equation}
\label{eqn-BinaryAccuracy}
\text{Accuracy} = \frac{TP + FN}{TP + FP + FN + FP}
\end{equation}

\paragraph*{}For a multi-class problem, we present accuracy over \textit{all} classes simultaneously. It is the ratio of the sum of the main diagonal to the sum or all entries in the matrix:
\begin{equation}
\label{eqn-AvgAccuracy}
\text{Accuracy} = \frac{\sum_{i}C_{i,i}}{\sum_{i}\sum_{j}C_{i,j}}
\end{equation}
Where all sum indexes goes from $0$ to $k-1$.

@@

\paragraph*{}To formally produce classification predictions on the chaotic synthesizer wave forms, we must use all of the principles outlined in the previous sections. Using the described features in sec. (\ref{sec-Features}) and appropriate architecture sec. (\ref{subsec-Architecture}), We run a

we produce a neural network \textit{ChaoticSynthClassifier} and train it on the roughly $18,000$ audio files that serve as the training set.
